Solar wind discontinuities spatial evolution in the outer heliosphere

### 2024-02-08 index.qmd
update

::: {.callout-note collapse="false"}
## Related works

@@

Spatial distribution of the discontinuities
:::
:::

>>>>

## Publications

- manuscript please see [here](_manuscript/index.html)
- AGU poster [here](presentations/AGU23_poster.qmd)

## Updates

::: {.column-screen layout-ncol="4"}
![](figures/new/current/current_k_r_dist)

![](figures/new/current/current_k_N1_r_dist)

![](figures/new/thickness/thickness_k_r_dist)

![](figures/new/thickness/thickness_k_N1_r_dist)

New
:::

::: {.column-screen layout-ncol="4"}

![](figures/current/current_r_dist)

![](figures/current/current_N1_r_dist)

![](figures/thickness/thickness_k_r_dist)

![](figures/thickness/thickness_k_N1_r_dist)

Old
:::

::: {.column-screen layout-nrow="1"}

![Wind](figures/ts_method/wind)

![Juno](figures/ts_method/juno)

![Derivative method](figures/ts_method/derivative)

![Fit method](figures/ts_method/fit)

:::

![](figures/ts_method/all)

<!-- ::: {.column-screen layout-nrow="1"}

![Effect of the time resolution on the discontinuity properties](figures/ts_effect_fit_new)

![Effect of the time resolution on the discontinuity properties](figures/ts_effect)

::: -->

## Related works

@@

Spatial distribution of the discontinuities
:::
